\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-02-02 correct.tex
Paper updates

\begin{theorem}
  Given \texttt{wait\_inbetween (M..N)} Algorithm~\ref{alg:1} gives a
  value \texttt{d}, provided $D$ is a non empty set, such that for any
  given reaction time $\hj{\Delta}$ \hj{in the range of} $BCRT \leq
  \Delta \leq WCRT$, $M \leq \Delta \times d \leq N$ holds.
\label{th:1}
\end{theorem}
\begin{proof}
  We use case analysis and contradiction to prove the above theorem.
  \begin{compactenum}[\hspace{0.25cm} 1.]
  \item Proof for case $\Delta = WCRT$: Assume \mbox{$d \times WCRT <
      M$}, then $d < \frac{M}{WCRT}$. $BCRT \leq WCRT$, by definition,
    hence, $\frac{M}{WCRT} \leq \frac{M}{BCRT}$. Thus for the assumption
    to hold, $d < \frac{M}{BCRT}$, which contradicts
    Lemma~\ref{lemma:1}. The assumption $d \times WCRT >N$ is trivially
    proven from Lemma~\ref{lemma:1}.
  \item Proof for case $\Delta = BCRT$: Like above, the assumption $d
    \times BCRT < M$ is trivially proven from Lemma~\ref{lemma:1}. For
    $d \times BCRT > N$ to hold, $d > \frac{N}{BCRT}$ should hold. But,
    $BCRT \leq WCRT$, by definition, hence, $\frac{N}{BCRT} \geq
    \frac{N}{WCRT}$, which again contradicts Lemma~\ref{lemma:1}.
  \item Proof for case $BCRT < \Delta < WCRT$: For $d \times \Delta < M$
    to hold, $d < \frac{M}{\Delta}$ should hold. By definition, $\Delta
    > BCRT$, thus, $\frac{M}{BCRT} < \frac{M}{\Delta}$, hence, $d <
    \frac{M}{BCRT}$ should hold, which contradicts Lemma~\ref{lemma:1}. We
    can prove the other case $d \times \Delta \leq N$, using the upper
    bound from Lemma~\ref{lemma:1} similarly.
  \end{compactenum}
\end{proof}

@@

\begin{proof}
  The proof is the opposite of case 3 in Theorem~\ref{th:1}.
\end{proof}

The proofs for correctness, completeness, and soundness for
Algorithm~\ref{alg:2} are similar to those of
Algorithm~\ref{alg:1}. Furthermore, even correctness, completeness, and
soundness for \texttt{wait\_atleast (M)} and \texttt{wait\_exact (M)}
can be proven using the same techniques as shown in Theorem~\ref{th:1}.

>>>>

\begin{theorem}
  Given \texttt{wait\_inbetween (M..N)} Algorithm~\ref{alg:1} gives a
  value \texttt{d}, provided $D$ is a non empty set, such that for any
  given reaction time $\hj{\Delta}$ \hj{in the range of} $BCRT \leq
  \Delta \leq WCRT$, $M \leq \Delta \times d \leq N$ holds.
\label{th:1}
\end{theorem}
\begin{proof}
  We use contradiction to prove the theorem.
  \begin{compactenum}[\hspace{0.25cm} 1.]
  \item Proof for case $\Delta = WCRT$: Assume \mbox{$d \times WCRT <
      M$}, then $d < \frac{M}{WCRT}$. $BCRT \leq WCRT$, by definition,
    hence, $\frac{M}{WCRT} \leq \frac{M}{BCRT}$. Thus for the assumption
    to hold, $d < \frac{M}{BCRT}$, which contradicts
    Lemma~\ref{lemma:1}. The assumption $d \times WCRT >N$ is trivially
    proven from Lemma~\ref{lemma:1}.
  \item Proof for case $\Delta = BCRT$: Like above, the assumption $d
    \times BCRT < M$ is trivially proven from Lemma~\ref{lemma:1}. For
    $d \times BCRT > N$ to hold, $d > \frac{N}{BCRT}$ should hold. But,
    $BCRT \leq WCRT$, by definition, hence, $\frac{N}{BCRT} \geq
    \frac{N}{WCRT}$, which again contradicts Lemma~\ref{lemma:1}.
  \item Proof for case $BCRT < \Delta < WCRT$: For $d \times \Delta < M$
    to hold, $d < \frac{M}{\Delta}$ should hold. By definition, $\Delta
    > BCRT$, thus, $\frac{M}{\Delta} < \frac{M}{BCRT}$, hence, $d <
    \frac{M}{BCRT}$ should hold, which contradicts
    Lemma~\ref{lemma:1}. We can prove the other case $d \times \Delta >
    N$, using the upper bound from Lemma~\ref{lemma:1} similarly.
  \end{compactenum}
\end{proof}

@@

\begin{proof}
  Soundness is trivially proven knowing that there exists no $\Delta <
  BCRT$ or $\Delta > WCRT$ by definition
  (cf. Section~\ref{sec:mapping-logical-time}).
\end{proof}

The proofs for correctness, completeness, and soundness for
Algorithm~\ref{alg:2} are similar to those of
Algorithm~\ref{alg:1}. Furthermore, correctness, completeness, and
soundness for \texttt{wait\_atleast (M)} and \texttt{wait\_exact (M)}
are dependent on Theorem~\ref{th:1}, because these are variants of the
\texttt{wait\_inbetween (M..N)} statement.

### 2014-02-02 delays.tex
Paper updates

Our algorithm takes as input: WCRT, BCRT, and the lower and upper bounds
$M$ and $N$, respectively, of the \texttt{wait\_inbetween} construct. We
first divide $M$ and $N$ with the BCRT and WCRT, respectively. This
division gives us the number of individual logical ticks required to
postpone the CD (or synchronous program) by the real-time
specification. We always $ceil$ when dividing $M$ and $floor$ when
dividing $N$ to make sure that the resultant values are integers (in
domain $\mathbb{N}^{>0}$) and these functions guarantee that the
resultant logical ticks result in real-time postponements between the
required range $[M,N]$. Next, a function $F$ maps these calculated
values to a set of equidistant integer points (values) separated by a
unit value -- these points represent all the logical ticks running at
the WCRT and the BCRT, respectively that satisfy the real-time wait
requirements. The intersection of these two sets gives all the logical
ticks that satisfy the real-time requirements invariant of the logical
time and its elasticity.

Let us revisit the HRTCS example (cf. Figure~\ref{fig:1}) to illustrate
the algorithm. From Figure~\ref{fig:1} we know that $M$ is 50.3 ms and
$N$ is 200.3 ms, respectively. \hj{Timing analysis of the program has
found} WCRT and BCRT be: 0.112 ms and 0.0334 ms, respectively. Thus, the
algorithm proceeds as follows:

@@

The aforementioned technique maintains the essence of synchronous and
GALS programs -- the logical tick, but in doing so is unable to provide
the exact real-time wait of $M$ time units in case of
\texttt{wait\_exact(M)} statement, or is unable to provide a
postponement in the region of $[M, N]$ time units in the case of
\texttt{wait\_inbetween (M..N)} statement, thereby violating their
semantics. The second option is to execute the CD periodically at the
WCRT. WCRT determines the fastest execution speed of any CD with the
guarantee that no input events from the environment will be missed
(cf. Section~\ref{sec:mapping-logical-time}). Thus, if we simply execute
the CD periodically at the WCRT, we can choose the value of \textit{d}
from set $S1$. This technique allows meeting the synchronous hypothesis,
while at the same time guaranteeing the semantics of the
\texttt{wait\_exact(M)} statement. But, compared to the previous option,
this technique is very inflexible and results in reduced response time
and increased power consumption.

>>>>

Our algorithm takes as input: WCRT, BCRT, and the lower and upper bounds
$M$ and $N$, respectively, of the \texttt{wait\_inbetween} construct. We
first divide $M$ and $N$ with the BCRT and WCRT, respectively. This
division gives us the number of individual logical ticks, at the fastest
(BCRT) and slowest (WCRT) program execution speeds, required to postpone
the CD (or synchronous program) by the real-time specification. We
always $ceil$ when dividing $M$ and $floor$ when dividing $N$ to make
sure that the resultant values are integers (in domain
$\mathbb{N}^{>0}$) and these functions guarantee that the resultant
logical ticks result in real-time postponements between the required
range $[M,N]$. Next, a function $F$ maps these calculated values to a
set of equidistant integer points (values) separated by a unit value --
these points represent all the logical ticks running at the WCRT and the
BCRT, respectively that satisfy the real-time wait requirements. The
intersection of these two sets gives all the logical ticks that satisfy
the real-time requirements invariant of the logical time and its
elasticity.

Let us revisit the HRTCS example (cf. Figure~\ref{fig:1}) to illustrate
the algorithm. From Figure~\ref{fig:1} we know that $M$ is 50.3 ms and
$N$ is 200.3 ms, respectively. \hj{Timing analysis of the program has
  found} WCRT and BCRT to be: 0.112 ms and 0.0334 ms,
respectively. Thus, the algorithm proceeds as follows:

@@

The aforementioned technique maintains the essence of synchronous and
GALS programs -- the logical tick, but in doing so is unable to provide
the exact real-time wait of $M$ time units in case of
\texttt{wait\_exact(M)} statement, or is unable to provide a
postponement in the region of $[M, N]$ time units in the case of
\texttt{wait\_inbetween (M..N)} statement, thereby violating their
semantics. The second option is to execute the CD periodically at the
WCRT. WCRT determines the fastest execution speed of any CD with the
guarantee that no input events from the environment will be missed
(cf. Section~\ref{sec:mapping-logical-time}). Thus, if we simply execute
the CD periodically at the WCRT, we can choose the value of \textit{d}
from set $S1$. This technique allows meeting the synchronous hypothesis,
while at the same time guaranteeing the semantics of the
\texttt{wait\_exact(M)} statement. This technique trades-off reduced
average reaction time and increased power consumption while providing
exact postponement.

### 2014-02-02 exps.tex
Paper updates

\hj{ Printer is an example from~\cite{Schneider:1999:CRT:555233}, which
models a printer and a spooler in timed CSP. Its operation can be
described as follows: as soon as the spooler receives a print job it
passes it to the printer through a channel where actual printing process
take place.} Each spooler and printer process is mapped to a separate
CD. Spooler CD sends a job to the Printer CD between 2.7 to 10.6 ms
after receiving it from the environment (e.g. a user). On the other
hand, Printer CD notifies the environment that it starts printing
between 1.2 to 30.3 ms once it receives the job from the Spooler CD.
Actual print job is started between 5.6 to 100.2 ms after the
notification. In this example, bounded wait ensures that both; channel
communication and print job should occur within the specified amount of
time. This example along with HRTCS demonstrates the use of non exact
wait statements.

AECS (Access and Environmental Control System) is an application that
controls an intelligent room environment described in~\cite{aecs_ispa}.
AECS has 2 CDs; CD1 consist of a single wait statement, while CD2 has 2
wait statements. The system is designed to measure how long the entrance
door to the room is being opened or to detect unknown entries (i.e.
intruders). For instance, the system triggers an alarm 10 seconds after
detection of an intruder or generates a beep sound when an entrance door
is being opened for the same amount of time. In the original AECS, the
system needed to interact with two external timers through input/output
signals in order to wait for a specific amount of time (e.g.
\texttt{TimerTriggered} in Figure~\ref{delaycode:a}). When the timer
expires, it notifies the system through the input signal
\texttt{TimeOut}, which is polled using the \texttt{await} statement.
The program has been modified such that the wait constructs replace
external timers and corresponding interface (I/O) signals, which is
shown in Figure~\ref{delaycode:b}.  With the new wait constructs, these
timers are not necessary and real-time waits can be expressed directly
in the SystemJ code.

@@

The previous results show that for HRTCS and Printer the compiler was
able to find \textit{d} without relaxing upper bound of wait
statements. Figure~\ref{fig:graph1} shows the accuracy of our results by
comparing between the programmer specified upper bounds
(Table~\ref{fig:benchlist}) and the actual bounds obtained using our
techniques (Table~\ref{fig:comparison}) for the examples requiring
relaxation. AECS/CD1 wait specification is not included in
Figure~\ref{fig:graph2}, because although it requires relaxation, the
wait specification (Table~\ref{fig:benchlist}) does not have an upper
bound.

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD2},
			height=5cm,
			width=9.5cm,
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
			ytick={0,0.5,...,2},
			enlarge x limits=0.3,
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
			{(HRTCS,1)(Printer/CD1,1)(Printer/CD2,1)(AECS/CD2,1.94)};
			\addplot + [black,fill=white,postaction={pattern=north west
                          lines}] coordinates 
                        {(Printer/CD2, 1)(AECS/CD2, 1.94)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor},
			ytick={0,0.5,...,5},
			ymin={1.5},
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
%      extra y ticks={2.5},
%      extra y tick labels={asdf},
%      extra y tick style={grid=major},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 2.60)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 2.63)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 4.39)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 2.92)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 2.69)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph1}
\end{figure}

There are two influential factors in determining the relaxation: 1)
execution speed of a target platform and 2) the nature of the program
that runs on this platform. Clock frequency of the processor directly
impacts the value of WCRT. On the other hand, programmer can write a
program such that large data (or control) computations in a single
logical tick increase WCRT of the program.  Assuming we do not change
the architecture of the execution platform (i.e. JOP), the difference
factor can only be reduced by modifying the benchmark programs such that
the critical paths are broken up using \texttt{pause} constructs,
thereby reducing the WCRT.  Figure~\ref{fig:improv} shows segments of
code from AECS whose WCRT is reduced by such technique.

\begin{figure}[h!]
	\centering
	\vspace{-10pt}
	\begin{SubFloat}{\label{fig:improv-a}Original program}
    \begin{minipage}[b]{0.45\linewidth}
		\begin{lstlisting}[style=sysj,morekeywords={present,emit,trap,pause,exit,delay,suspend}]
present(EntryRequest)
  id = #EntryRequest;
else
  id = #ExitRequest;
if(E.isValiedRequest(id)){
  // code ..
}
\end{lstlisting}
\end{minipage}
\end{SubFloat}
  \begin{SubFloat}{\label{fig:improv-b}Program with reduced WCRT}
    \centering
    \begin{minipage}[b]{0.45\linewidth}
		\begin{lstlisting}[style=sysj,morekeywords={emit,present,trap,pause,exit,delay,suspend}]
present(EntryRequest)
  id = #EntryRequest;
else
  id = #ExitRequest;
pause; // Inserting pause
if(E.isValiedRequest(id)){
  // code ..
}
\end{lstlisting}
		\end{minipage}
	\end{SubFloat}
	\caption{Improving WCRT by shortening a critical path}
	\label{fig:improv}
	\vspace{-10pt}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00) (AECS/CD2, 11.82)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}

>>>>

\hj{ Printer is an example from~\cite{Schneider:1999:CRT:555233}, which
models a printer and a spooler in timed CSP. Its operation can be
described as follows: as soon as the spooler receives a print job it
passes it to the printer through a channel where actual printing process
take place.} Each spooler and printer process is mapped to a separate
CD. Spooler CD sends a job to the Printer CD between 2.7 to 10.6 ms
after receiving it from the environment (e.g. a user). On the other
hand, Printer CD notifies the environment that it starts printing
between 1.2 to 30.3 ms once it receives the job from the Spooler CD.
Actual print job is started between 5.6 to 100.2 ms after the
notification. In this example, bounded wait ensures that both; channel
communication and print job should occur within the specified amount of
time. % This example along with HRTCS demonstrates the use of non exact
% wait statements.

AECS (Access and Environmental Control System) is an application that
controls an intelligent room environment described in~\cite{aecs_ispa}.
AECS has 2 CDs; each with one wait statement. The system is designed to
measure how long the entrance door to the room is being opened or to
detect unknown entries (i.e.  intruders). For instance, the system
triggers an alarm 10 seconds after detection of an intruder or generates
a beep sound when an entrance door is being opened for the same amount
of time. In the original AECS, the system needed to interact with two
external timers through input/output signals in order to wait for a
specific amount of time (e.g.  \texttt{TimerTriggered} in
Figure~\ref{delaycode:a}). When the timer expires, it notifies the
system through the input signal \texttt{TimeOut}, which is polled using
the \texttt{await} statement.  The program has been modified such that
the wait constructs replace external timers and corresponding interface
(I/O) signals, which is shown in Figure~\ref{delaycode:b}.  With the new
wait constructs, these timers are not necessary and real-time waits can
be expressed directly in the SystemJ code.

@@

The previous results show that for HRTCS and Printer the compiler was
able to find \textit{d} without relaxing upper bound of wait
statements. Figure~\ref{fig:graph1} shows the accuracy of our results by
comparing between the programmer specified upper bounds
(Table~\ref{fig:benchlist}) and the actual bounds obtained using our
techniques (Table~\ref{fig:comparison}).
% relaxation. % AECS/CD1 wait specification is not included in
% Figure~\ref{fig:graph1}, because although it requires relaxation, the
% wait specification (Table~\ref{fig:benchlist}) does not have an upper
% bound.

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD1,AECS/CD2},
			height=5cm,
			width=9.5cm,
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
			ytick={0,0.5,...,2},
			enlarge x limits=0.3,
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
			{(HRTCS,1)(Printer/CD1,1)(Printer/CD2,0)(AECS/CD1,1)(AECS/CD2,0)};
			\addplot + [black,fill=white,postaction={pattern=north west
                          lines}] coordinates 
                        {(Printer/CD2, 1)(AECS/CD2, 1.94)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor},
			ytick={0,0.5,...,5},
			ymin={1.5},
			minor y tick num=1,
			yminorgrids=true,
			ymajorgrids=true,
%      extra y ticks={2.5},
%      extra y tick labels={asdf},
%      extra y tick style={grid=major},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 2.60)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 2.63)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 4.39)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 2.92)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 2.69)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph1}
\end{figure}

There are two influential factors in determining the relaxation: 1)
execution speed of a target platform and 2) the nature of the program
that runs on this platform. Clock frequency of the processor directly
impacts the value of WCRT. On the other hand, programmer can write a
program such that large data (or control) computations in a single
logical tick increase WCRT of the program.  Assuming we do not change
the architecture of the execution platform (i.e. JOP), the difference
factor can only be reduced by modifying the benchmark programs such that
the critical paths are broken up using additional \texttt{pause}
constructs, thereby reducing the WCRT.  Figure~\ref{fig:improv} shows
segments of code from AECS whose WCRT is reduced by such technique.

\begin{figure}[h!]
	\centering
	\vspace{-10pt}
	\begin{SubFloat}{\label{fig:improv-a}Original program}
    \begin{minipage}[b]{0.45\linewidth}
		\begin{lstlisting}[style=sysj,morekeywords={present,emit,trap,pause,exit,delay,suspend}]
present(EntryRequest)
// obtaining signal value
  id = #EntryRequest;
else
  id = #ExitRequest;
if(E.isValiedRequest(id)){
  // code ..
}
\end{lstlisting}
\end{minipage}
\end{SubFloat}
  \begin{SubFloat}{\label{fig:improv-b}Program with reduced WCRT}
    \centering
    \begin{minipage}[b]{0.45\linewidth}
		\begin{lstlisting}[style=sysj,morekeywords={emit,present,trap,pause,exit,delay,suspend}]
present(EntryRequest)
  id = #EntryRequest;
else
  id = #ExitRequest;
pause; // Inserting pause
if(E.isValiedRequest(id)){
  // code ..
}
\end{lstlisting}
		\end{minipage}
	\end{SubFloat}
	\caption{Improving WCRT by shortening a critical path}
	\label{fig:improv}
	\vspace{-10pt}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
%\begin{tikzpicture}[scale=0.9]
%  \begin{axis}[
%      ybar,xtick=data,
%      symbolic x
%      coords={AECS/CD2},
%      height=5cm,
%      width=9.5cm,
%      minor y tick num=1,
%      yminorgrids=true,
%      ymajorgrids=true,
%      xlabel=Benchmark,
%      ylabel=Percentage reduction,
%    ]
%      \addplot coordinates
%      {(AECS/CD2, 11.82)};
%  \end{axis}
%\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x coords={Motor,AECS/CD2},
			ytick={0,1,...,12},
			ymin={6},
			minor y tick num=1,
			enlarge x limits=0.5,
			enlarge y limits=0.1,
			yminorgrids=true,
			ymajorgrids=true,
			height=7cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Percentage reduction (\%),
			legend style={
				anchor=north,
				at={(0.45,-0.29)},
				legend columns=-1,
			}
		]
			\addplot + [black,fill=white,postaction={pattern=north east lines}] coordinates
                        {(Motor, 8.05) (AECS/CD2, 11.82)};
			\addplot + [black,fill=white,postaction={pattern=north west lines}] coordinates
                        {(Motor, 8.00)};
			\addplot + [black,fill=white,postaction={pattern=dots}] coordinates
                        {(Motor, 6.42)};
			\addplot + [black,fill=white,postaction={pattern=horizontal lines}] coordinates
                        {(Motor, 7.53)};
			\addplot + [black,fill=white,postaction={pattern=crosshatch}] coordinates
                        {(Motor, 7.89)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Reduction in upper bound relaxation with improved WCRT}
\label{fig:graph2}
\end{figure}

### 2014-02-02 introduction.tex
Paper updates

Reactive languages~\cite{gber931,amal10} are a class of programming
languages used for designing and implementing reactive systems, which
continuously respond to input from their environment. These languages
have been successfully used in programming a plethora of systems such as
fly-by-wire in Airbus~\cite{eairbus}, security surveillance
systems~\cite{amal121}, etc. Usually these systems also need to meet
real-time constraints imposed by the environment. Yet, these languages
do not support describing real-time statements as first class language
constructs.  For example, one cannot describe a simple real-time delay
(postponement) of an operation for 0.2 ms. These languages are based on
formal semantics, essential for correct by construction code generation
and verification of correctness of functional properties of the
developed programs, but leave nonfunctional properties such as timing
behavior as an implementation detail~\cite{boldt07}. Arguably, rightly
so, because physical time cannot be incorporated without information
about the underlying execution platform.  But, one can still reason in
terms of logical time. These languages support discrete logical clock
rather than a discrete physical (real-time) clock. The real-time period
of the discrete logical clock (also referred to as a logical tick) is
not fixed and it is determined by the responsiveness of the program to
the input signals. Unlike a discrete physical clock, which has fixed
real-time period, the period of the logical clock is elastic. Although
the timing model with logical clock has worked well for reactive
synchronous/GALS languages in designing discrete systems, there is a
need to introduce real-time since often, implementation models are in
the continuous or discrete real-time
domain~\cite{DBLP:journals/pieee/SifakisTY03}.  Moreover, adding timing
capabilities as first class language constructs create additional
opportunity for formally verifying functional and non-functional
requirements before system deployment.

@@

The major motivations for introducing these real-time \textit{wait}
mechanisms and at the same time \textbf{contributions} of the paper are:
\hj{(1) real-time wait does not affect the model of logical time in
  SystemJ program as long as the amount of delay is within boundaries
  that can be determined statically by program analysis, assuming that
  real-time analyzable platforms are available,} (2) the waiting model
relies on the use of relative instead of absolute real-time, i.e., a
wait in selected time units is counted from the currently executing
SystemJ statement and (3) these waiting mechanisms allow mixing
behaviors with real-time features and others with only logical time. All
these as well as semantics of the wait constructs are discussed and
illustrated in the rest of the paper. Our contributions can be further
refined as follows:

\begin{enumerate*}
\item Real-time is modeled in the $\mathbb{Q}^{>0}$ domain of numbers,
 i.e., non-negative rational numbers.
% \item We consider the property of \textit{non
%     maximal-parallelism}. \textit{Non-maximal parallelism:} There are
%   not always sufficient resources for processes to execute, so
%   effectively processes are allocated and scheduled with different
%   optimization criteria -- reducing computation time, reducing power
%   consumption, etc. This allocation and scheduling is an integral part
%   of any language compilation and needs to be considered when
%   introducing real-time waits.
\item We are the first, to our knowledge, to allow specification of
  both; exact and non-exact real-time in GALS and synchronous programs.
\item We shed light upon a key insight relating real-time and
  logical-time -- \textit{the resolution of any real-time statement is
    dependent on the worst case logical tick time} -- an aspect that
  seems to have escaped in the current literature on incorporation of
  real-time in synchronous/GALS languages.
\end{enumerate*}

The rest of the paper is arranged as follows:
Section~\ref{sec:background} gives the background on SystemJ and related
techniques required for the rest of the
paper. Section~\ref{sec:intr-real-time} introduces real-time mechanisms
in the GALS paradigm and describes their compilation into logical
time. Section~\ref{sec:proof-correctness} sketches the correctness
proofs for the introduced
algorithms. Section~\ref{sec:experimental-results} gives the
experimental results for a set of real-time applications. In
Section~\ref{sec:disc-perc-limit} we discuss the advantages and
limitations of the proposed approach. Section~\ref{sec:related-work}
positions this work in relation to other approaches to introducing
real-time. Finally, we conclude in Section~\ref{sec:concl-future-work}.

>>>>

Reactive languages~\cite{gber931,amal10} are a class of programming
languages used for designing and implementing reactive systems, which
continuously respond to input from their environment. These languages
have been successfully used in programming a plethora of systems such as
fly-by-wire in Airbus~\cite{eairbus}, security surveillance
systems~\cite{amal121}, etc. Usually these systems also need to meet
real-time constraints imposed by the environment. Yet, these languages
do not support describing real-time statements as first class language
constructs.  For example, one cannot describe a simple real-time delay
(postponement) of an operation for 0.2 ms. These languages are based on
formal semantics, essential for correct by construction code generation
and formally verifying functional properties of developed programs, but
leave nonfunctional properties such as timing behavior as an
implementation detail~\cite{boldt07}. Arguably, rightly so, because
physical time cannot be incorporated without information about the
underlying execution platform.  But, one can still reason in terms of
logical time. These languages support discrete logical clock rather than
a discrete physical (real-time) clock. The real-time period of the
discrete logical clock (also referred to as a logical tick) is not fixed
and it is determined by the speed of computation of the program for
different input signals. Unlike a discrete physical clock, which has
fixed real-time period, the period of the logical clock is
elastic. Although the timing model with logical clock has worked well
for reactive synchronous/GALS languages in designing discrete systems,
there is a need to introduce real-time since often, implementation
models are in the continuous or discrete real-time
domain~\cite{DBLP:journals/pieee/SifakisTY03}.  Moreover, adding timing
capabilities as first class language constructs create additional
opportunity for formally verifying functional and non-functional
requirements before system deployment.

@@

The major motivations for introducing these real-time \textit{wait}
mechanisms and at the same time \textbf{contributions} of the paper are:
\hj{(1) real-time wait does not affect the model of logical time in
  SystemJ program as long as the amount of delay is within boundaries
  that can be determined statically by program analysis, assuming that
  real-time analyzable platforms are available,} (2) the waiting model
relies on the use of relative instead of absolute real-time, i.e., a
wait in selected time units is counted from the beginning of the wait
statement and (3) these waiting mechanisms allow mixing behaviors with
real-time features and others with only logical time. All these as well
as semantics of the wait constructs are discussed and illustrated in the
rest of the paper. Our contributions can be further refined as follows:

\begin{enumerate*}
\item Real-time is specified in the $\mathbb{Q}^{>0}$ domain of numbers,
  i.e., non-negative rational numbers.
% \item We consider the property of \textit{non
%     maximal-parallelism}. \textit{Non-maximal parallelism:} There are
%   not always sufficient resources for processes to execute, so
%   effectively processes are allocated and scheduled with different
%   optimization criteria -- reducing computation time, reducing power
%   consumption, etc. This allocation and scheduling is an integral part
%   of any language compilation and needs to be considered when
%   introducing real-time waits.
\item We are the first, to our knowledge, to allow specification of
  both; exact and non-exact real-time in GALS and synchronous programs.
\item We shed light upon a key insight relating real-time and
  logical-time -- \textit{the resolution of any real-time statement is
    dependent on the worst case logical tick time} -- an aspect that
  seems to have escaped in the current literature on incorporation of
  real-time in synchronous/GALS languages.
\end{enumerate*}

The rest of the paper is arranged as follows:
Section~\ref{sec:background} gives the background on SystemJ and related
techniques required for the rest of the
paper. Section~\ref{sec:intr-real-time} introduces real-time mechanisms
in the GALS paradigm and describes their compilation into logical
time. Section~\ref{sec:proof-correctness} sketches the correctness
proofs for the introduced
algorithms. Section~\ref{sec:experimental-results} gives the
experimental results for a set of real-time applications. In
Section~\ref{sec:disc-perc-limit} we discuss the advantages and
limitations of the proposed approach. Section~\ref{sec:related-work}
positions this work in relation to other approaches to introducing
real-time in other languages. Finally, we conclude in
Section~\ref{sec:concl-future-work}.
